Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-12 paper/main.tex
comment
Light abstract editing

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% AV, AD: operationalization
In this study, we explore different ways to operationalize spatial perception in
14 subjects that were watching an audio-visual Hollywood movie and listened to
the movie's audio-description (studyforrest.org).
% auditory localizer?
Focussing on the audio-description, we further test if an auditory narrative
could localize a ``visual area'' in individual subjects.
% GLM
For each naturalistic stimulus, we model hemodynamic activity via several
general linear model (GLM) $t$-contrasts that are based on stimulus annotations
/ selected stimulus features.
% VIS
Current results are compared to results of classic visual localizer experiment
that we conducted previously to localize the PPA in the same participants
\citep{sengupata2016extension}.
% results: group AV
On a group level, results of our current approach to operationalize the
perception of space during a movie reveal significantly increased hemodynamic
activity spatially overlapping with the PPA but also extending into early visual
cortices.
% results: group AD
Results of the audio-description reveal significant activation restricted to the
anterior part of the PPA.
% results: individual AD
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in two subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
an audio-visual movie and an exclusively auditory stimulus.
% conclusion: PPA has subregions
Our results provides further evidence that the PPA can be divided into
functional subregions.
% localizer substitute
An auditory narrative might substitute a visual paradigm to localize the PPAs
anterior part in visually impaired subjects.\todo{very bold claim to be written
in the abstract}

>>>>

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% AV, AD: operationalization
In this study, we explore different ways to operationalize spatial perception\todo{not sure if this is just perception} in
14 subjects that were watching an audio-visual Hollywood movie and listened to
the movie's audio-description (studyforrest.org).
% auditory localizer?
Focussing on the audio-description, we test if an auditory narrative
could localize a ``visual area'' in individual subjects.
% GLM
For each naturalistic stimulus, we model hemodynamic activity via several
general linear model (GLM) $t$-contrasts that are based on annotations
of selected stimulus features.
% VIS
Current results are compared to results of classic visual localizer experiment
that we conducted previously to localize the PPA in the same participants.
% no refs in abstract (probably)
%\citep{sengupata2016extension}.
% results: group AV
On a group level, results for a visual movie stimulus show significantly increased hemodynamic
activity spatially overlapping with a traditionally localized PPA but also extending into earlier visual
cortices.
% results: group AD
Results for the audio-description stimulus reveal significant activation restricted to the
anterior part of the PPA.
% results: individual AD
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in two subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
an audio-visual movie and an exclusively auditory stimulus.
% conclusion: PPA has subregions
Our results provides further evidence that the PPA can be divided into
functional subregions.
% localizer substitute
An auditory narrative might substitute a visual paradigm to localize the PPAs
anterior part in visually impaired subjects.\todo{very bold claim to be written
in the abstract}
